---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
pkgload::load_all(export_all = FALSE)
```

# vibrrt

<!-- badges: start -->
[![vibrrt status badge](https://paithiov909.r-universe.dev/badges/vibrrt)](https://paithiov909.r-universe.dev)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/paithiov909/vibrrt/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/paithiov909/vibrrt/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

An R wrapper for [vibrato](https://github.com/daac-tools/vibrato): Viterbi-based accelerated tokenizer.

## Installation

To install from source package, the Rust toolchain is required.

```r
install.packages("vibrrt", repos = c("https://paithiov909.r-universe.dev", "https://cloud.r-project.org"))
```

## Usage

You can download the model files from [ryan-minato/vibrato-models](https://huggingface.co/ryan-minato/vibrato-models)
using [hfhub](https://github.com/mlverse/hfhub) package.


```{r}
sample_text <- jsonlite::read_json(
  "https://paithiov909.r-universe.dev/gibasa/data/ginga/json",
  simplifyVector = TRUE
)

# withr::with_envvar(c(HUGGINGFACE_HUB_CACHE = tempdir()), {
ipadic <- hfhub::hub_download("ryan-minato/vibrato-models", "ipadic-mecab-2_7_0/system.dic")
# })

vibrrt::tokenize(
  sample_text[5:8],
  tagger = vibrrt::create_tagger(ipadic)
)
```

## Versioning

This package is versioned by copying the version number of [vibrato](https://github.com/daac-tools/vibrato),
where the first three digits represent that version number
and the fourth digit (if any) represents the patch release for this package.
